\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2017-01-05 redaction/dhp_sept2016.tex

Our first contribution to the literature is to provide estimates for the size of both the ad-valorem and the additive components of transport costs. Table \ref{tab:summary_results} reports a summary of our results. It displays the mean and median values of each type of trade costs (ad-valorem estimated alone, estimated along with additive costs and the additive component), as well as the associated standard deviation, averaged over the period 1974-2013, for estimation driven both at the 3- and 4-digit sectorial level.\footnote{In Appendix \ref{app:more_results}, we report similar results for a sample of years, for both transport mode, at the 3 and 4-digit classification level. Results for all years (available at the 3-digit level) are available upon request to the authors. We investigate the evolution of transport costs over the period in more details in Section \ref{sec:results_decomposition}.}$^{,}$\footnote{We present the results for air at the 3-digit level removing the year 1989, as the estimation results reveal the presence of strong outliers that bias the estimates of transport costs upwards. Overall results (over the whole period) are not substantially affected if this year is included though. These results are available upon request to the authors.}

>>>>

Our first contribution to the literature is to provide estimates for the size of both the ad-valorem and the additive components of transport costs. Table \ref{tab:summary_results} reports a summary of our results. It displays the mean and median values of each type of trade costs  (ad-valorem estimated alone, estimated along with additive costs and the additive component), as well as the associated standard deviation, averaged over the period 1974-2013, for estimation driven both at the 3- and 4-digit sectorial level for different specifications and data. The first panel reports the results for a specification based on ad-valorem costs estimated alone, while the second panel presents estimates for a specification involving both ad-valorem and multiplicative component. Finally, the third panel reports the same set of descriptive statistics, but for the actual cif/fas ratio in our data.\footnote{In Appendix \ref{app:more_results}, we report similar results for a sample of years, for both transport mode, at the 3 and 4-digit classification level. Results for all years (available at the 3-digit level) are available upon request to the authors.}$^{,}$\footnote{We present the results for air at the 3-digit level removing the year 1989, as the estimation results reveal the presence of strong outliers that bias the estimates of transport costs upwards. Overall results (over the whole period) are not substantially affected if this year is included though. These results are available upon request to the authors.}
